---
title: "Add Sites to Phospho Data"
output: html_notebook
---

##### This Notebook is written to parse phosphorylation substrate residues and positions from a spectronaut output and corresponding fasta file and to rewrite this information with the spectronaut data for use with MS Stats

To run, change file locations on lines 30-32 and potentially bp_utils file location on line 18. Make sure your version of the "LocatePeptidePtmInProteins.R" script in bp_utils is from Feb 2023 or newer. 


```{r, Dependencies}
library (data.table)
rotate.x.axis.text <- theme(axis.text.x = element_text(angle = 90))
library (magrittr)

# Change filepath below to location of bp_utils folder
# "~bp_utils\\" will work if this notebook is in the same directory as bp_utils folder-- IF YOU'RE ON MAC, make sure to use "/" file separator, not "\\"
utils <- "~bp_utils\\"
source(paste0(utils,"ManageScriptData.R"))
WriteSessionInfo()
WriteInstalledPackages()

```


##### Name Input and Output Files Here

```{r, Params}

specOutFile <-  ""    # Spectronaut output
fastaFile <- ""       # fasta file 
outputFile <- ""      # output file with site information

```


```{r, Locate Sites}

specFile <- fread(specOutFile)
specFile[, ProteinName := gsub(">","",ProteinName)]
fwrite(specFile,specOutFile)

source (paste0(utils,"LocatePeptidePtmInProteins.R"))

sitifyProteins_SpectronautFile(spec = specFile, fastaFile = fastaFile) # this changes the spec table, no need to catch the return value

# peptides without phospho as well as proteins that are not in FASTA will get an NA in oldProteinName (because their proteinName is not changed)
# I could handle this better, but this is what you get for now.
# Best to exclude these
spec <- spec[!is.na(spec$oldProteinName)]

fwrite(spec, outputFile)

```